### 2012-04-12 docs/architecture/architecture.tex
add constants

Problems piece together various \maestro\ directories, choosing a
reaction network, equation of state, and conductivity routine to build
an executable.  Briefly, the \maestro\ sub-directories are:
\begin{itemize}
\item {\tt data\_processing/}

  Simple Fortran-based analysis routines (e.g.\ extract a line from a
  multidimensional dataset) that operate on BoxLib datasets.  These are
  described in \S~\ref{sec:analysis}.

  Several sub-directories with python-based routines are also here.
  These are described both in \S~\ref{sec:analysis} and \S~\ref{sec:vis:python}.

\item {\tt extern/}

@@

@@

\subsection{\tt average}

The {\tt average} module provides a routine {\tt average} that takes
a multilevel \multifab\ array and averages the full Cartesian data
onto the 1D base state.

@@

>>>>

Problems piece together various \maestro\ directories, choosing a
reaction network, equation of state, and conductivity routine to build
an executable.  Briefly, the \maestro\ sub-directories are:
\begin{itemize}
\item {\tt extern/}

@@

Finally the {\tt AmrPostprocessing} package provides simple
Fortran-based analysis routines (e.g.\ extract a line from a
multidimensional dataset) that operate on BoxLib datasets.  These are
described in \S~\ref{sec:analysis}.  Several sub-directories with
python-based routines are also here.  These are described both in
\S~\ref{sec:analysis} and \S~\ref{sec:vis:python}.

@@

\subsection{\tt average\_module}

The {\tt average\_module} module provides a routine {\tt average} that takes
a multilevel \multifab\ array and averages the full Cartesian data
onto the 1D base state.

@@

\subsection{\tt fundamental\_constants\_module}

The {\tt fundamental\_constants\_module} provides a simple list of
various fundamental constants (e.g.\ Newton's gravitational constant)
in CGS units.
